### 2018-03-27 submission/manuscript.Rmd
reoword first intro paragraph

Accounting for bias is critical in order to reach an understanding of bacterial community changes using 16S rRNA gene sequencing results. First, it is important to differentiate between bias, reproducibility, and standardization since often times these three can be confused and used interchangeably with each other. Bias can change the observed results in a way that is reproducible and standardized. For example, if one group uses one brand of DNA extraction kit for their 16S rRNA gene sequencing, their results may be biased versus another group not using the same brand kit but within their group they can still have reproducible results. Therefore, standardization of 16S rRNA gene sequencing methods to increase reproducibility can still be problematic due to bias. Determining how different aspects of a 16S rRNA gene sequencing workflow could bias the observed results is critical for the interpretation of specific studies in the broader context of the overall field.

>>>>

Accounting for bias is critical in order to reach an understanding of bacterial community changes using 16S rRNA gene sequencing results. Differentiating between bias, reproducibility, and standardization is important since often times these three can be confused and used interchangeably with each other. Bias can change the observed results in a way that is reproducible and standardized. For example, if one group uses one brand of DNA extraction kit for their 16S rRNA gene sequencing, their results may be biased versus another group not using the same brand kit but within their group they can still have reproducible results [@contamination_Salter2014]. Our 16S rRNA gene sequencing methods are biased even when these workflows are standardized to increase reproducibility. In order to interpret specific studies within the broader context of the overall field, assessing bias at different parts of the 16S rRNA gene sequencing workflow is critical.
